Transferability of clinical prediction models for early trauma care

### 2019-10-09 ManuscriptMarkdownAJE.Rmd
Update and rename ManuscriptMarkdownAnon.Rmd to ManuscriptMarkdownAJE.Rmd

---
title: "Transferability of clinical prediction models for early trauma care"
date: "October 08, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

  *Background:* Trauma results in approximately four million deaths annually. Clinical
  prediction models are often used for triage in early trauma care. Transferring these 
  models between different settings might adversely affect model performance.

  *Methods:* Patients aged 15 years or older, registered between 2011-2016 
  in the Swedish national trauma registry, were included. Three data sets 
  were created: high- and low-volume centres, metropolitan and
  non-metropolitan centres, and multiple and single centres. Clinical
  prediction models were developed using logistic regression, and transferred within sets. 
  Model performance was evaluated in all data sets using the mistriage rate, undertriage 
  rate and overtriage rate. Model performance was reported as medians with the 95% uncertainty 
  interval across imputed data sets.

  *Results:* `r total.number.of.patients ` patients were included. Transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r highest.tran.mistriage`, 
  across all samples. The worst performance after transfer was the low-volume model 
  transferred to the high-volume sample, resulting in a significant mistriage rate 
  increase of `r highest.comp.mistriage`.

  *Conclusions:* In all samples, model transfer was associated with some uncertainty. 
  Models developed in samples with high numbers of patients generally performed best after 
  transfer, and the model developed in the low-volume sample performed worst after transfer.

>>>>

---
title: "Transferability of clinical prediction models for early trauma care"
date: "October 09, 2019"
documentclass: "article"
output:
  word_document:
    reference_docx: transferstyle.docx
header-includes:
   - \usepackage{hyperref}
bibliography: library.bib
csl: bmcemerg.csl
---
```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)

@@

  *Background:* Trauma results in approximately four million deaths annually. Clinical
  prediction models are often used for triage in early trauma care. This study aimed to 
  assess how transfers of clinical prediction models for early trauma 
  care between different care contexts within a single health system affected mistriage rates.

  *Methods:* Patients aged 15 years or older, registered between 2011-2016 
  in the Swedish national trauma registry, were included. Three data sets 
  were created: high- and low-volume centres, metropolitan and
  non-metropolitan centres, and multiple and single centres. Clinical
  prediction models were developed using logistic regression, and transferred within sets. 
  Model performance was evaluated in all data sets using mistriage rate, undertriage 
  rate and overtriage rate. Model performance was reported as medians with the 95% uncertainty 
  interval across imputed data sets.

  *Results:* `r total.number.of.patients ` patients were included. Transferred model
  mistriage rate ranged from `r lowest.tran.mistriage` to `r highest.tran.mistriage`. 
  Transfer of the low-volume model to the high-volume sample resulted in a significant 
  mistriage rate increase of `r highest.comp.mistriage`.

  *Conclusions:* Models developed in samples with high numbers of patients generally performed best after 
  transfer, and the model developed in the low-volume sample performed significantly worse after transfer.
